---
title: "E-Commerce Churn Analysis"
author: "Farhanul Haque"
date: "2026-06-25"
output: html_document
---

# — Data Understanding

# Step 1: Loading libraries.

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)   # data manipulation + ggplot2
library(lubridate)   # date handling
library(skimr)       # quick data summary
```

# Step 2: Data Loading....

```{r load-data, message=FALSE}
# All files except geolocation( due to big data )
customers  = read_csv("archive/olist_customers_dataset.csv")
orders     = read_csv("archive/olist_orders_dataset.csv")
items      = read_csv("archive/olist_order_items_dataset.csv")
payments   = read_csv("archive/olist_order_payments_dataset.csv")
reviews    = read_csv("archive/olist_order_reviews_dataset.csv")
products   = read_csv("archive/olist_products_dataset.csv")
sellers    = read_csv("archive/olist_sellers_dataset.csv")
cat_names  = read_csv("archive/product_category_name_translation.csv")

# Confirm: 
cat("Customers: ", nrow(customers), "rows\n")
cat("Orders:    ", nrow(orders),    "rows\n")
cat("Items:     ", nrow(items),     "rows\n")
cat("Payments:  ", nrow(payments),  "rows\n")
cat("Reviews:   ", nrow(reviews),   "rows\n")
cat("Products:  ", nrow(products),  "rows\n")
cat("Sellers:   ", nrow(sellers),   "rows\n")
```

# Step 3: Understanding part

# Customers Table
```{r explore-customers}
glimpse(customers)
```

# Orders Table
```{r explore-orders}
glimpse(orders)
```

# Order Items Table
```{r explore-items}
glimpse(items)
```

# Payments Table
```{r explore-payments}
glimpse(payments)
```

# Reviews Table
```{r explore-reviews}
glimpse(reviews)
```

# Products Table
```{r explore-products}
glimpse(products)
```

# Sellers Table
```{r explore-sellers}
glimpse(sellers)
```

# Step 4: Missing Values Check..

```{r missing-values}
# Har table mein missing values kitni hain
missing_summary = function(df, name) {
  df %>%
    summarise(across(everything(), ~sum(is.na(.)))) %>%
    pivot_longer(everything(),
                 names_to  = "column",
                 values_to = "missing_count") %>%
    filter(missing_count > 0) %>%
    mutate(table = name,
           missing_pct = round(missing_count / nrow(df) * 100, 2))
}

# Checking for tables
bind_rows(
  missing_summary(customers, "customers"),
  missing_summary(orders,    "orders"),
  missing_summary(items,     "items"),
  missing_summary(payments,  "payments"),
  missing_summary(reviews,   "reviews"),
  missing_summary(products,  "products"),
  missing_summary(sellers,   "sellers")
) %>%
  arrange(table, desc(missing_count)) %>%
  print(n = 50)
```

# Step 5: Time ranges of orders.

```{r time-range}
orders %>%
  summarise(
    earliest_order = min(order_purchase_timestamp, na.rm = TRUE),
    latest_order   = max(order_purchase_timestamp, na.rm = TRUE),
    total_days     = as.numeric(
                       difftime(
                         max(order_purchase_timestamp, na.rm = TRUE),
                         min(order_purchase_timestamp, na.rm = TRUE),
                         units = "days"
                       )
                     )
  )
```

# Step 6: Order Status Distribution

```{r order-status}
orders %>%
  count(order_status, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 2))
```

# Step 7: Verifying Table Relationships 

```{r relationships}
# Verify relationships between tables
cat("Unique customer_ids in customers table:", 
    n_distinct(customers$customer_id), "\n")

cat("Unique customer_ids in orders table:   ", 
    n_distinct(orders$customer_id), "\n")

cat("\nUnique order_ids in orders table:     ", 
    n_distinct(orders$order_id), "\n")

cat("Unique order_ids in items table:      ", 
    n_distinct(items$order_id), "\n")

cat("Unique order_ids in payments table:   ", 
    n_distinct(payments$order_id), "\n")

cat("Unique order_ids in reviews table:    ", 
    n_distinct(reviews$order_id), "\n")
```

# Phase 3 — Data Cleaning

## Step 1: Keeping Only Delivered Orders

```{r filter-delivered}
# Only delivered orders — 96,478 orders
orders_clean = orders %>%
  filter(order_status == "delivered")

cat("Orders after filtering:", nrow(orders_clean), "\n")
```

## Step 2: Translate Product Categories to English

```{r translate-categories}
products_clean = products %>%
  left_join(cat_names, by = "product_category_name") %>%
  mutate(category = coalesce(product_category_name_english,
                             product_category_name))
```

## Step 3: Build Master Dataframe

```{r master-dataframe}
master = orders_clean %>%
  # attach customer info
  left_join(customers, by = "customer_id") %>%
  # attach items (price, product)
  left_join(items %>%
              group_by(order_id) %>%
              summarise(
                order_value    = sum(price + freight_value),
                total_items    = n()
              ),
            by = "order_id") %>%
  # attach payment type
  left_join(payments %>%
              group_by(order_id) %>%
              slice(1) %>%
              select(order_id, payment_type),
            by = "order_id") %>%
  # attach review score
  left_join(reviews %>%
              group_by(order_id) %>%
              slice(1) %>%
              select(order_id, review_score),
            by = "order_id") %>%
  # keep only useful columns
  select(
    order_id,
    customer_unique_id,
    customer_state,
    customer_city,
    order_purchase_timestamp,
    order_delivered_customer_date,
    order_estimated_delivery_date,
    order_value,
    total_items,
    payment_type,
    review_score
  )

cat("Master dataframe rows:", nrow(master), "\n")
cat("Master dataframe columns:", ncol(master), "\n")
```

## Step 4: Add Useful Columns

```{r add-columns}
master = master %>%
  mutate(
    # extract year and month for cohort analysis later
    order_month = floor_date(order_purchase_timestamp, "month"),
    order_year  = year(order_purchase_timestamp),

    # delivery delay in days (negative = early delivery)
    delivery_delay = as.numeric(
      difftime(order_delivered_customer_date,
               order_estimated_delivery_date,
               units = "days")
    ),

    # was delivery late?
    is_late = delivery_delay > 0
  )
```

## Step 5: Final Check

```{r final-check}
cat("Total orders in master:", nrow(master), "\n")
cat("Unique customers:      ", length(unique(master$customer_unique_id)), "\n")
cat("Date range:            ",
    format(min(master$order_purchase_timestamp)), "to",
    format(max(master$order_purchase_timestamp)), "\n")

# Missing values in master
master %>%
  summarise(across(everything(), ~sum(is.na(.)))) %>%
  pivot_longer(everything(),
               names_to  = "column",
               values_to = "missing") %>%
  filter(missing > 0)
```

# Phase 4 — Exploratory Data Analysis (EDA)

## Plot 1: Orders Per Month

```{r orders-per-month}
master %>%
  count(order_month) %>%
  ggplot(aes(x = order_month, y = n)) +
  geom_line(color = "#2196F3", linewidth = 1) +
  geom_point(color = "#2196F3", size = 2) +
  labs(
    title    = "Orders Per Month (2016–2018)",
    subtitle = "Overall business growth trend",
    x        = "Month",
    y        = "Number of Orders"
  ) +
  theme_minimal()
```

## Plot 2: Top 10 States by Orders

```{r top-states}
master %>%
  count(customer_state, sort = TRUE) %>%
  slice(1:10) %>%
  ggplot(aes(x = reorder(customer_state, n), y = n)) +
  geom_col(fill = "#4CAF50") +
  coord_flip() +
  labs(
    title = "Top 10 States by Number of Orders",
    x     = "State",
    y     = "Orders"
  ) +
  theme_minimal()
```

## Plot 3: Order Value Distribution

```{r order-value-dist}
master %>%
  filter(!is.na(order_value), order_value < 500) %>%
  ggplot(aes(x = order_value)) +
  geom_histogram(bins = 50, fill = "#9C27B0", color = "white") +
  labs(
    title    = "Order Value Distribution",
    subtitle = "Orders above R$500 excluded for clarity",
    x        = "Order Value (R$)",
    y        = "Count"
  ) +
  theme_minimal()
```

## Plot 4: Payment Types

```{r payment-types}
master %>%
  filter(!is.na(payment_type)) %>%
  count(payment_type, sort = TRUE) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  ggplot(aes(x = reorder(payment_type, n), y = n)) +
  geom_col(fill = "#FF9800") +
  geom_text(aes(label = paste0(pct, "%")),
            hjust = -0.1, size = 3.5) +
  coord_flip() +
  labs(
    title = "Payment Type Distribution",
    x     = "Payment Type",
    y     = "Orders"
  ) +
  theme_minimal()
```

## Plot 5: Review Score Distribution

```{r review-scores}
master %>%
  filter(!is.na(review_score)) %>%
  count(review_score) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  ggplot(aes(x = factor(review_score), y = n,
             fill = factor(review_score))) +
  geom_col() +
  geom_text(aes(label = paste0(pct, "%")),
            vjust = -0.5, size = 3.5) +
  scale_fill_manual(values = c(
    "1" = "#F44336",
    "2" = "#FF9800",
    "3" = "#FFC107",
    "4" = "#8BC34A",
    "5" = "#4CAF50"
  )) +
  labs(
    title = "Review Score Distribution",
    x     = "Review Score",
    y     = "Count"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## Plot 6: Delivery Performance

```{r delivery-performance}
master %>%
  filter(!is.na(is_late)) %>%
  count(is_late) %>%
  mutate(
    label = ifelse(is_late, "Late", "On Time"),
    pct   = round(n / sum(n) * 100, 1)
  ) %>%
  ggplot(aes(x = label, y = n, fill = label)) +
  geom_col() +
  geom_text(aes(label = paste0(pct, "%")),
            vjust = -0.5, size = 4) +
  scale_fill_manual(values = c(
    "On Time" = "#4CAF50",
    "Late"    = "#F44336"
  )) +
  labs(
    title = "Delivery Performance",
    x     = "",
    y     = "Orders"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## Key EDA Summary Stats

```{r eda-summary}
cat("Average order value:  R$", 
    round(mean(master$order_value, na.rm = TRUE), 2), "\n")

cat("Median order value:   R$", 
    round(median(master$order_value, na.rm = TRUE), 2), "\n")

cat("Average review score:", 
    round(mean(master$review_score, na.rm = TRUE), 2), "\n")

cat("Late deliveries:     ", 
    round(mean(master$is_late, na.rm = TRUE) * 100, 1), "%\n")

cat("Most used payment:   ", 
    master %>% 
      count(payment_type, sort = TRUE) %>% 
      slice(1) %>% 
      pull(payment_type), "\n")
```
# Phase 5 — Customer Analytics

## Step 1: Repeat vs One-Time Buyers

```{r repeat-vs-onetime}
customer_orders = master %>%
  group_by(customer_unique_id) %>%
  summarise(
    total_orders    = n(),
    total_spent     = sum(order_value, na.rm = TRUE),
    avg_order_value = mean(order_value, na.rm = TRUE),
    first_order     = min(order_purchase_timestamp),
    last_order      = max(order_purchase_timestamp),
    avg_review      = mean(review_score, na.rm = TRUE)
  ) %>%
  mutate(
    customer_type = ifelse(total_orders == 1, 
                           "One-Time", 
                           "Repeat")
  )

# Summary
customer_orders %>%
  count(customer_type) %>%
  mutate(percentage = round(n / sum(n) * 100, 2))
```

## Step 2: Visualize One-Time vs Repeat

```{r plot-customer-type}
customer_orders %>%
  count(customer_type) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  ggplot(aes(x = customer_type, y = n, fill = customer_type)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = paste0(pct, "%\n(", n, ")")),
            vjust = -0.3, size = 4) +
  scale_fill_manual(values = c(
    "One-Time" = "#F44336",
    "Repeat"   = "#4CAF50"
  )) +
  labs(
    title    = "One-Time vs Repeat Customers",
    subtitle = "How many customers came back?",
    x        = "",
    y        = "Number of Customers"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## Step 3: Purchase Frequency Distribution

```{r purchase-frequency}
customer_orders %>%
  filter(total_orders <= 10) %>%
  count(total_orders) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  ggplot(aes(x = factor(total_orders), y = n)) +
  geom_col(fill = "#2196F3") +
  geom_text(aes(label = paste0(pct, "%")),
            vjust = -0.5, size = 3.5) +
  labs(
    title    = "Purchase Frequency Distribution",
    subtitle = "How many orders did each customer place?",
    x        = "Number of Orders",
    y        = "Number of Customers"
  ) +
  theme_minimal()
```

## Step 4: Time Between First and Second Order

```{r time-to-second-order}
# Only repeat customers
time_to_second = master %>%
  group_by(customer_unique_id) %>%
  arrange(order_purchase_timestamp) %>%
  mutate(order_rank = row_number()) %>%
  filter(order_rank <= 2) %>%
  summarise(
    days_to_second = as.numeric(
      difftime(
        max(order_purchase_timestamp),
        min(order_purchase_timestamp),
        units = "days"
      )
    ),
    .groups = "drop"
  ) %>%
  filter(days_to_second > 0)  # only repeat customers

cat("Avg days to second order:", 
    round(mean(time_to_second$days_to_second), 1), "\n")
cat("Median days to second order:", 
    round(median(time_to_second$days_to_second), 1), "\n")

# Plot
time_to_second %>%
  filter(days_to_second <= 365) %>%
  ggplot(aes(x = days_to_second)) +
  geom_histogram(bins = 30, fill = "#9C27B0", color = "white") +
  geom_vline(xintercept = median(time_to_second$days_to_second),
             color = "red", linetype = "dashed", linewidth = 1) +
  annotate("text",
           x    = median(time_to_second$days_to_second) + 15,
           y    = Inf,
           label = paste0("Median: ",
                          round(median(time_to_second$days_to_second)),
                          " days"),
           vjust = 2, hjust = 0, color = "red") +
  labs(
    title    = "Days Between First and Second Order",
    subtitle = "Among repeat customers only",
    x        = "Days",
    y        = "Count"
  ) +
  theme_minimal()
```

## Step 5: Revenue by Customer Type

```{r revenue-by-type}
customer_orders %>%
  group_by(customer_type) %>%
  summarise(
    customers       = n(),
    total_revenue   = round(sum(total_spent, na.rm = TRUE), 0),
    avg_spent       = round(mean(total_spent, na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  mutate(revenue_pct = round(total_revenue / sum(total_revenue) * 100, 1))
```

## Step 6: Customer Analytics Summary

```{r customer-summary}
cat("Total unique customers:     ", nrow(customer_orders), "\n")
cat("One-time buyers:            ", 
    sum(customer_orders$customer_type == "One-Time"), "\n")
cat("Repeat buyers:              ", 
    sum(customer_orders$customer_type == "Repeat"), "\n")
cat("Repeat rate:                ", 
    round(mean(customer_orders$customer_type == "Repeat") * 100, 2), 
    "%\n")
cat("Max orders by one customer: ", 
    max(customer_orders$total_orders), "\n")
cat("Avg spend - One-Time:    R$",
    round(mean(customer_orders$total_spent[
      customer_orders$customer_type == "One-Time"], 
      na.rm = TRUE), 2), "\n")
cat("Avg spend - Repeat:      R$",
    round(mean(customer_orders$total_spent[
      customer_orders$customer_type == "Repeat"], 
      na.rm = TRUE), 2), "\n")
```
# Phase 6 — Churn Analysis

## Step 1: Define Churn Label

```{r define-churn}
# Reference date = last date in dataset
reference_date = max(master$order_purchase_timestamp, 
                      na.rm = TRUE)

cat("Reference date:", format(reference_date), "\n")

# Label each customer as churned or retained
churn_data = customer_orders %>%
  mutate(
    days_since_last_order = as.numeric(
      difftime(reference_date, last_order, units = "days")
    ),
    churned = ifelse(days_since_last_order > 180, 1, 0),
    churn_label = ifelse(churned == 1, "Churned", "Retained")
  )

# Overall churn rate
churn_data %>%
  count(churn_label) %>%
  mutate(percentage = round(n / sum(n) * 100, 2))
```

## Step 2: Visualize Churn Rate

```{r plot-churn-rate}
churn_data %>%
  count(churn_label) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  ggplot(aes(x = churn_label, y = n, fill = churn_label)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = paste0(pct, "%\n(", n, ")")),
            vjust = -0.3, size = 4) +
  scale_fill_manual(values = c(
    "Churned"  = "#F44336",
    "Retained" = "#4CAF50"
  )) +
  labs(
    title    = "Customer Churn Rate",
    subtitle = "Churned = no order in 180 days",
    x        = "",
    y        = "Number of Customers"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## Step 3: Churn vs Review Score

```{r churn-vs-review}
# Join churn data with master for review scores
churn_review = master %>%
  group_by(customer_unique_id) %>%
  summarise(
    avg_review = mean(review_score, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(churn_data %>% 
              select(customer_unique_id, churn_label),
            by = "customer_unique_id") %>%
  filter(!is.na(avg_review), !is.na(churn_label))

# Average review score by churn status
churn_review %>%
  group_by(churn_label) %>%
  summarise(
    avg_review_score = round(mean(avg_review), 2),
    customers        = n(),
    .groups = "drop"
  )
```

```{r plot-churn-review}
churn_review %>%
  ggplot(aes(x = factor(round(avg_review)), 
             fill = churn_label)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c(
    "Churned"  = "#F44336",
    "Retained" = "#4CAF50"
  )) +
  labs(
    title    = "Churn Rate by Review Score",
    subtitle = "Do unhappy customers churn more?",
    x        = "Review Score",
    y        = "Proportion",
    fill     = ""
  ) +
  theme_minimal()
```

## Step 4: Churn vs Delivery Delay

```{r churn-vs-delivery}
churn_delivery = master %>%
  group_by(customer_unique_id) %>%
  summarise(
    avg_delay = mean(delivery_delay, na.rm = TRUE),
    was_late  = any(is_late, na.rm = TRUE),
    .groups   = "drop"
  ) %>%
  left_join(churn_data %>%
              select(customer_unique_id, churn_label),
            by = "customer_unique_id") %>%
  filter(!is.na(churn_label))

# Late delivery churn rate vs on-time
churn_delivery %>%
  filter(!is.na(was_late)) %>%
  group_by(was_late, churn_label) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(was_late) %>%
  mutate(
    pct        = round(n / sum(n) * 100, 2),
    late_label = ifelse(was_late, "Late Delivery", "On Time")
  )
```

```{r plot-churn-delivery}
churn_delivery %>%
  filter(!is.na(was_late)) %>%
  mutate(late_label = ifelse(was_late, 
                             "Late Delivery", 
                             "On Time")) %>%
  ggplot(aes(x = late_label, fill = churn_label)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c(
    "Churned"  = "#F44336",
    "Retained" = "#4CAF50"
  )) +
  labs(
    title    = "Churn Rate: Late vs On-Time Delivery",
    subtitle = "Does late delivery increase churn?",
    x        = "",
    y        = "Proportion",
    fill     = ""
  ) +
  theme_minimal()
```

## Step 5: Churn vs Order Value

```{r churn-vs-ordervalue}
churn_data %>%
  filter(!is.na(avg_order_value)) %>%
  mutate(
    value_segment = case_when(
      avg_order_value < 50   ~ "Low (<R$50)",
      avg_order_value < 150  ~ "Medium (R$50-150)",
      avg_order_value < 300  ~ "High (R$150-300)",
      TRUE                   ~ "Premium (>R$300)"
    ),
    value_segment = factor(value_segment, levels = c(
      "Low (<R$50)", "Medium (R$50-150)",
      "High (R$150-300)", "Premium (>R$300)"
    ))
  ) %>%
  group_by(value_segment, churn_label) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(value_segment) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  ggplot(aes(x = value_segment, y = pct, 
             fill = churn_label)) +
  geom_col() +
  geom_text(aes(label = paste0(pct, "%")),
            position = position_stack(vjust = 0.5),
            size = 3.5, color = "white") +
  scale_fill_manual(values = c(
    "Churned"  = "#F44336",
    "Retained" = "#4CAF50"
  )) +
  labs(
    title = "Churn Rate by Order Value Segment",
    x     = "Order Value Segment",
    y     = "Percentage",
    fill  = ""
  ) +
  theme_minimal()
```

## Step 6: Churn Summary

```{r churn-summary}
total     = nrow(churn_data)
churned   = sum(churn_data$churned == 1)
retained  = sum(churn_data$churned == 0)

cat("Total customers:    ", total, "\n")
cat("Churned:            ", churned,
    "(", round(churned/total*100, 1), "%)\n")
cat("Retained:           ", retained,
    "(", round(retained/total*100, 1), "%)\n")

cat("\nAvg review - Churned:  ",
    round(mean(churn_review$avg_review[
      churn_review$churn_label == "Churned"], 
      na.rm = TRUE), 2), "\n")

cat("Avg review - Retained: ",
    round(mean(churn_review$avg_review[
      churn_review$churn_label == "Retained"], 
      na.rm = TRUE), 2), "\n")
```
# Phase 7 — Cohort Analysis

## Step 1: Build Cohort Table

```{r cohort-setup}
# Step 1: Assign cohort month to each customer
# Cohort = month of first ever purchase
cohort_data <- master %>%
  group_by(customer_unique_id) %>%
  mutate(
    cohort_month = floor_date(
      min(order_purchase_timestamp), "month"
    )
  ) %>%
  ungroup()

# Step 2: Calculate order month number
# (how many months after first purchase)
cohort_data <- cohort_data %>%
  mutate(
    order_month_date = floor_date(
      order_purchase_timestamp, "month"
    ),
    month_number = as.integer(
      interval(cohort_month, order_month_date) %/% months(1)
    )
  )

# Step 3: Count unique customers per cohort per month
cohort_table <- cohort_data %>%
  group_by(cohort_month, month_number) %>%
  summarise(
    customers = n_distinct(customer_unique_id),
    .groups   = "drop"
  )

# Step 4: Get cohort sizes (month 0 = starting size)
cohort_size <- cohort_table %>%
  filter(month_number == 0) %>%
  select(cohort_month, cohort_size = customers)

# Step 5: Calculate retention percentage
cohort_pct <- cohort_table %>%
  left_join(cohort_size, by = "cohort_month") %>%
  mutate(
    retention_pct = round(customers / cohort_size * 100, 1)
  ) %>%
  filter(
    cohort_month >= as.Date("2017-01-01"),
    cohort_month <= as.Date("2018-04-01"),
    month_number  <= 12
  )

cat("Cohort table built successfully\n")
cat("Cohorts:", n_distinct(cohort_pct$cohort_month), "\n")
```

## Step 2: Retention Heatmap

```{r cohort-heatmap, fig.width=12, fig.height=8}
cohort_pct %>%
  mutate(
    cohort_label = format(cohort_month, "%b %Y")
  ) %>%
  ggplot(aes(
    x    = factor(month_number),
    y    = reorder(cohort_label, desc(cohort_month)),
    fill = retention_pct
  )) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(
    aes(label = paste0(retention_pct, "%")),
    size  = 3,
    color = ifelse(cohort_pct$retention_pct > 20, 
                   "white", "black")
  ) +
  scale_fill_gradient2(
    low      = "#FFEBEE",
    mid      = "#EF9A9A",
    high     = "#B71C1C",
    midpoint = 10,
    name     = "Retention %"
  ) +
  labs(
    title    = "Customer Retention Cohort Analysis",
    subtitle = "% of customers returning each month after first purchase",
    x        = "Months After First Purchase",
    y        = "Cohort (First Purchase Month)"
  ) +
  theme_minimal() +
  theme(
    axis.text  = element_text(size = 9),
    plot.title = element_text(size = 14, face = "bold")
  )
```

## Step 3: Month 1 Retention by Cohort

```{r month1-retention}
# How many came back in month 1?
month1 = cohort_pct %>%
  filter(month_number == 1) %>%
  arrange(desc(retention_pct)) %>%
  mutate(cohort_label = format(cohort_month, "%b %Y"))

cat("Average Month 1 retention:", 
    round(mean(month1$retention_pct), 2), "%\n")
cat("Best cohort: ", 
    month1$cohort_label[1], "→",
    month1$retention_pct[1], "%\n")
cat("Worst cohort:", 
    month1$cohort_label[nrow(month1)], "→",
    month1$retention_pct[nrow(month1)], "%\n")
```

```{r plot-month1}
month1 %>%
  ggplot(aes(
    x    = reorder(cohort_label, retention_pct),
    y    = retention_pct,
    fill = retention_pct
  )) +
  geom_col() +
  geom_text(aes(label = paste0(retention_pct, "%")),
            hjust = -0.1, size = 3.5) +
  coord_flip() +
  scale_fill_gradient(
    low  = "#FFCDD2",
    high = "#C62828"
  ) +
  labs(
    title    = "Month 1 Retention Rate by Cohort",
    subtitle = "What % came back the very next month?",
    x        = "Cohort",
    y        = "Retention %"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## Step 4: Overall Retention Curve

```{r retention-curve}
retention_curve <- cohort_pct %>%
  group_by(month_number) %>%
  summarise(
    avg_retention = round(mean(retention_pct), 2),
    .groups = "drop"
  )

retention_curve %>%
  ggplot(aes(x = month_number, y = avg_retention)) +
  geom_line(color = "#C62828", linewidth = 1.2) +
  geom_point(color = "#C62828", size = 3) +
  geom_text(aes(label = paste0(avg_retention, "%")),
            vjust = -0.8, size = 3.5) +
  scale_x_continuous(breaks = 0:12) +
  labs(
    title    = "Average Retention Curve",
    subtitle = "How quickly do customers drop off?",
    x        = "Months After First Purchase",
    y        = "Avg Retention %"
  ) +
  theme_minimal()
```

## Step 5: Cohort Summary

```{r cohort-summary}
cat("=== Cohort Analysis Summary ===\n\n")

cat("Month 0 retention:  100% (baseline)\n")

cat("Month 1 avg retention:", 
    retention_curve$avg_retention[
      retention_curve$month_number == 1], "%\n")

cat("Month 3 avg retention:", 
    retention_curve$avg_retention[
      retention_curve$month_number == 3], "%\n")

cat("Month 6 avg retention:", 
    retention_curve$avg_retention[
      retention_curve$month_number == 6], "%\n")

cat("Month 12 avg retention:", 
    retention_curve$avg_retention[
      retention_curve$month_number == 12], "%\n")
```
# Phase 8 — RFM Segmentation

## Step 1: Calculate RFM Scores

```{r rfm-calculate}
reference_date = max(master$order_purchase_timestamp, 
                      na.rm = TRUE)

rfm_data = master %>%
  group_by(customer_unique_id) %>%
  summarise(
    recency   = as.numeric(difftime(
                  reference_date,
                  max(order_purchase_timestamp),
                  units = "days")),
    frequency = n(),
    monetary  = sum(order_value, na.rm = TRUE),
    .groups   = "drop"
  )

cat("RFM base table built\n")
cat("Total customers:", nrow(rfm_data), "\n")
glimpse(rfm_data)
```

## Step 2: Score Each Customer 1–5

```{r rfm-scoring}
rfm_scored = rfm_data %>%
  mutate(
    # Recency: lower days = better = higher score
    r_score = ntile(desc(recency),  5),
    # Frequency: higher = better = higher score
    f_score = ntile(frequency, 5),
    # Monetary: higher = better = higher score
    m_score = ntile(monetary,  5),
    # Combined RFM score
    rfm_score = r_score + f_score + m_score
  )

cat("Score distribution:\n")
summary(rfm_scored$rfm_score)
```

## Step 3: Assign Segments

```{r rfm-segments}
rfm_scored = rfm_scored %>%
  mutate(
    segment = case_when(
      r_score >= 4 & f_score >= 4 & m_score >= 4 ~ "Champions",
      r_score >= 3 & f_score >= 3                ~ "Loyal Customers",
      r_score >= 4 & f_score <= 2                ~ "Potential Loyalists",
      r_score >= 3 & f_score <= 2 & m_score >= 3 ~ "Promising",
      r_score <= 2 & f_score >= 3                ~ "At Risk",
      r_score <= 2 & f_score <= 2 & m_score >= 3 ~ "Cant Lose Them",
      r_score == 1 & f_score == 1                ~ "Lost",
      TRUE                                        ~ "Need Attention"
    )
  )

# Segment distribution
rfm_scored %>%
  count(segment, sort = TRUE) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))
```

## Step 4: Visualize Segments

```{r plot-rfm-segments}
rfm_scored %>%
  count(segment) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  ggplot(aes(
    x    = reorder(segment, n),
    y    = n,
    fill = segment
  )) +
  geom_col() +
  geom_text(aes(label = paste0(pct, "%\n(", n, ")")),
            hjust = -0.05, size = 3.5) +
  coord_flip() +
  scale_fill_manual(values = c(
    "Champions"          = "#1B5E20",
    "Loyal Customers"    = "#388E3C",
    "Potential Loyalists"= "#81C784",
    "Promising"          = "#FFF176",
    "Need Attention"     = "#FFB74D",
    "At Risk"            = "#EF6C00",
    "Cant Lose Them"     = "#F44336",
    "Lost"               = "#B71C1C"
  )) +
  labs(
    title    = "RFM Customer Segments",
    subtitle = "Customer distribution across segments",
    x        = "",
    y        = "Number of Customers"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## Step 5: Segment Revenue Analysis

```{r rfm-revenue}
segment_revenue = rfm_scored %>%
  group_by(segment) %>%
  summarise(
    customers     = n(),
    total_revenue = round(sum(monetary), 0),
    avg_revenue   = round(mean(monetary), 2),
    avg_recency   = round(mean(recency), 0),
    avg_frequency = round(mean(frequency), 2),
    .groups = "drop"
  ) %>%
  mutate(
    revenue_pct = round(total_revenue / 
                        sum(total_revenue) * 100, 1)
  ) %>%
  arrange(desc(total_revenue))

print(segment_revenue)
```

## Step 6: RFM Score Heatmap

```{r rfm-heatmap, fig.width=8, fig.height=6}
rfm_scored %>%
  group_by(r_score, f_score) %>%
  summarise(
    avg_monetary = mean(monetary),
    customers    = n(),
    .groups      = "drop"
  ) %>%
  ggplot(aes(
    x    = factor(f_score),
    y    = factor(r_score),
    fill = avg_monetary
  )) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = round(avg_monetary, 0)),
            size = 3.5) +
  scale_fill_gradient(
    low  = "#E3F2FD",
    high = "#1565C0",
    name = "Avg Revenue (R$)"
  ) +
  labs(
    title    = "RFM Score Heatmap",
    subtitle = "Average revenue by Recency vs Frequency score",
    x        = "Frequency Score (1=Low, 5=High)",
    y        = "Recency Score (1=Old, 5=Recent)"
  ) +
  theme_minimal()
```

## Step 7: Champions vs Lost — Deep Comparison

```{r champions-vs-lost}
rfm_scored %>%
  filter(segment %in% c("Champions", "Lost")) %>%
  group_by(segment) %>%
  summarise(
    customers     = n(),
    avg_recency   = round(mean(recency), 1),
    avg_frequency = round(mean(frequency), 2),
    avg_monetary  = round(mean(monetary), 2),
    total_revenue = round(sum(monetary), 0),
    .groups       = "drop"
  )
```

## Step 8: RFM Summary

```{r rfm-summary}
cat("=== RFM Segmentation Summary ===\n\n")

cat("Total customers segmented:", nrow(rfm_scored), "\n\n")

top_segment <- rfm_scored %>%
  count(segment, sort = TRUE) %>%
  slice(1)

cat("Largest segment:", top_segment$segment,
    "(", top_segment$n, "customers )\n")

champions <- rfm_scored %>% 
  filter(segment == "Champions")
cat("\nChampions count:", nrow(champions), "\n")
cat("Champions avg spend: R$",
    round(mean(champions$monetary), 2), "\n")
cat("Champions avg orders:",
    round(mean(champions$frequency), 2), "\n")

lost <- rfm_scored %>% 
  filter(segment == "Lost")
cat("\nLost customers:", nrow(lost), "\n")
cat("Lost avg spend: R$",
    round(mean(lost$monetary), 2), "\n")
```
# Phase 9 — Customer Lifetime Value (CLV)

## Step 1: Calculate CLV Per Customer

```{r clv-calculate}
# Dataset span in years
dataset_days  = as.numeric(difftime(
  max(master$order_purchase_timestamp, na.rm = TRUE),
  min(master$order_purchase_timestamp, na.rm = TRUE),
  units = "days"
))
dataset_years = dataset_days / 365

cat("Dataset spans:", round(dataset_years, 2), "years\n\n")

# CLV per customer
clv_data = rfm_scored %>%
  mutate(
    # Average order value
    avg_order_value = monetary / frequency,
    
    # Purchase frequency per year
    frequency_per_year = frequency / dataset_years,
    
    # Customer lifespan in years
    # (days between first and last order / 365)
    lifespan_years = case_when(
      frequency == 1 ~ 0.5,  # one-time = assume 6 months
      TRUE ~ as.numeric(difftime(
        max(master$order_purchase_timestamp, na.rm = TRUE),
        min(master$order_purchase_timestamp, na.rm = TRUE),
        units = "days"
      )) / 365
    ),
    
    # CLV = AOV × Frequency/year × Lifespan
    clv = avg_order_value * frequency_per_year * lifespan_years
  )

cat("CLV calculated for", nrow(clv_data), "customers\n")
summary(clv_data$clv)
```

## Step 2: CLV by Segment

```{r clv-by-segment}
clv_segment = clv_data %>%
  group_by(segment) %>%
  summarise(
    customers    = n(),
    avg_clv      = round(mean(clv, na.rm = TRUE), 2),
    median_clv   = round(median(clv, na.rm = TRUE), 2),
    total_clv    = round(sum(clv, na.rm = TRUE), 0),
    avg_monetary = round(mean(monetary, na.rm = TRUE), 2),
    .groups      = "drop"
  ) %>%
  arrange(desc(avg_clv))

print(clv_segment)
```

## Step 3: Visualize CLV by Segment

```{r plot-clv-segment, fig.width=10, fig.height=6}
clv_segment %>%
  ggplot(aes(
    x    = reorder(segment, avg_clv),
    y    = avg_clv,
    fill = segment
  )) +
  geom_col() +
  geom_text(aes(label = paste0("R$", avg_clv)),
            hjust = -0.1, size = 3.5) +
  coord_flip() +
  scale_fill_manual(values = c(
    "Champions"           = "#1B5E20",
    "Loyal Customers"     = "#388E3C",
    "Potential Loyalists" = "#81C784",
    "Promising"           = "#FFF176",
    "Need Attention"      = "#FFB74D",
    "At Risk"             = "#EF6C00",
    "Cant Lose Them"      = "#F44336",
    "Lost"                = "#B71C1C"
  )) +
  labs(
    title    = "Average Customer Lifetime Value by Segment",
    subtitle = "Which segments are most valuable?",
    x        = "",
    y        = "Average CLV (R$)"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## Step 4: Revenue at Risk Calculation

```{r revenue-at-risk}
# At Risk + Cant Lose Them = immediate danger
at_risk_clv = clv_data %>%
  filter(segment %in% c("At Risk", "Cant Lose Them")) %>%
  summarise(
    customers       = n(),
    total_clv       = round(sum(clv), 0),
    avg_clv         = round(mean(clv), 2),
    total_revenue   = round(sum(monetary), 0),
    .groups         = "drop"
  )

cat("=== Revenue At Risk ===\n")
cat("At Risk + Cant Lose Them customers:",
    at_risk_clv$customers, "\n")
cat("Their historical revenue:    R$",
    at_risk_clv$total_revenue, "\n")
cat("Their projected CLV:         R$",
    at_risk_clv$total_clv, "\n")
```

## Step 5: CLV Uplift If At Risk Recovered

```{r clv-uplift}
# What if we convert At Risk to Champions?
champions_avg_clv = clv_segment %>%
  filter(segment == "Champions") %>%
  pull(avg_clv)

at_risk_count = clv_data %>%
  filter(segment == "At Risk") %>%
  nrow()

cant_lose_count = clv_data %>%
  filter(segment == "Cant Lose Them") %>%
  nrow()

at_risk_avg_clv = clv_segment %>%
  filter(segment == "At Risk") %>%
  pull(avg_clv)

cant_lose_avg_clv = clv_segment %>%
  filter(segment == "Cant Lose Them") %>%
  pull(avg_clv)

# Uplift calculation
uplift_at_risk = at_risk_count * 
                  (champions_avg_clv - at_risk_avg_clv)

uplift_cant_lose = cant_lose_count * 
                    (champions_avg_clv - cant_lose_avg_clv)

cat("=== CLV Uplift Potential ===\n\n")
cat("If At Risk → Champions:\n")
cat("  Customers:", at_risk_count, "\n")
cat("  CLV uplift: R$", round(uplift_at_risk, 0), "\n\n")

cat("If Cant Lose Them → Champions:\n")
cat("  Customers:", cant_lose_count, "\n")
cat("  CLV uplift: R$", round(uplift_cant_lose, 0), "\n\n")

cat("Total potential CLV uplift: R$",
    round(uplift_at_risk + uplift_cant_lose, 0), "\n")
```

## Step 6: CLV Distribution Plot

```{r plot-clv-distribution}
clv_data %>%
  filter(clv < quantile(clv, 0.95)) %>%
  ggplot(aes(x = clv, fill = segment)) +
  geom_histogram(bins = 40, color = "white") +
  scale_fill_manual(values = c(
    "Champions"           = "#1B5E20",
    "Loyal Customers"     = "#388E3C",
    "Potential Loyalists" = "#81C784",
    "Promising"           = "#FFF176",
    "Need Attention"      = "#FFB74D",
    "At Risk"             = "#EF6C00",
    "Cant Lose Them"      = "#F44336",
    "Lost"                = "#B71C1C"
  )) +
  labs(
    title    = "CLV Distribution by Segment",
    subtitle = "Top 5% excluded for clarity",
    x        = "Customer Lifetime Value (R$)",
    y        = "Count",
    fill     = "Segment"
  ) +
  theme_minimal()
```

## Step 7: CLV Summary

```{r clv-summary}
cat("=== CLV Summary ===\n\n")

cat("Overall avg CLV:     R$",
    round(mean(clv_data$clv, na.rm = TRUE), 2), "\n")

cat("Overall median CLV:  R$",
    round(median(clv_data$clv, na.rm = TRUE), 2), "\n")

champions_clv <- clv_segment %>%
  filter(segment == "Champions") %>%
  pull(avg_clv)

lost_clv <- clv_segment %>%
  filter(segment == "Lost") %>%
  pull(avg_clv)

cat("\nChampions avg CLV:   R$", champions_clv, "\n")
cat("Lost avg CLV:        R$", lost_clv, "\n")
cat("Champions vs Lost:   ",
    round(champions_clv / lost_clv, 1),
    "x more valuable\n")

cat("\nTotal platform CLV:  R$",
    round(sum(clv_data$clv, na.rm = TRUE), 0), "\n")
```
# Phase 11 — Business Recommendations

## Overview

This analysis of 93,358 customers and 96,478 
delivered orders (Sept 2016 – Oct 2018) reveals 
that Olist faces a fundamental customer retention 
challenge. The following recommendations are 
derived directly from the data findings across 
all analytical phases.

---

## Key Findings Summary

```{r findings-summary}
findings <- data.frame(
  Finding = c(
    "One-Time Buyer Rate",
    "Overall Churn Rate (180 days)",
    "Month 1 Cohort Retention",
    "Repeat Customer Avg Spend vs One-Time",
    "Champions vs Lost CLV Gap",
    "Revenue at Risk (At Risk + Cant Lose Them)",
    "CLV Uplift Potential"
  ),
  Value = c(
    "97%",
    "59.2%",
    "0.47%",
    "R$308 vs R$160 (92% more)",
    "8.6x",
    "R$ 5,821,138",
    "R$ 2,077,785"
  ),
  Implication = c(
    "Platform loyalty nearly non-existent",
    "Majority of customers do not return",
    "Almost no customer returns next month",
    "Repeat buyers are significantly more valuable",
    "Retaining top customers is critical",
    "High-value customers are disengaging",
    "Recoverable if action taken now"
  )
)

knitr::kable(findings, 
             caption = "Key Findings at a Glance")
```

---

## Recommendation 1 — Launch a Loyalty Program

**Priority: HIGH**

**Based on:** 97% one-time buyer rate, 
repeat customers spend 92% more

**The Problem:**

Customers have no incentive to return to 
Olist specifically. They are satisfied with 
their purchase but feel no platform attachment. 
Review scores average 4.16/5 — the experience 
is good, but nothing pulls them back.

**The Recommendation:**

Introduce an "Olist Points" loyalty program 
where customers earn points on every purchase 
redeemable for discounts on future orders.

```{r loyalty-impact}
# Estimated impact if repeat rate improves
current_repeat    = 0.03
target_repeat     = 0.08   # conservative 8% target
total_customers   = 93358
avg_repeat_spend  = 308.53
avg_onetime_spend = 160.73

additional_repeats = total_customers * 
                      (target_repeat - current_repeat)

revenue_uplift = additional_repeats * 
                  (avg_repeat_spend - avg_onetime_spend)

cat("Current repeat rate:       ", 
    current_repeat * 100, "%\n")
cat("Target repeat rate:        ", 
    target_repeat * 100, "%\n")
cat("Additional repeat customers:", 
    round(additional_repeats), "\n")
cat("Estimated revenue uplift:  R$", 
    round(revenue_uplift, 0), "\n")
```

---

## Recommendation 2 — Target At Risk Segment Immediately

**Priority: HIGH**

**Based on:** At Risk = 22,311 customers, 
R$3.7M historical revenue, 394 days inactive

**The Problem:**

The At Risk segment is the single largest 
revenue-generating group — yet they have not 
purchased in over 13 months on average. 
Every day without action increases permanent 
churn probability.

**The Recommendation:**

Launch a targeted win-back campaign 
specifically for At Risk customers:

```{r atrisk-breakdown}
at_risk_stats = churn_data %>%
  left_join(
    rfm_scored %>% select(customer_unique_id, segment),
    by = "customer_unique_id"
  ) %>%
  filter(segment == "At Risk") %>%
  summarise(
    customers         = n(),
    avg_days_inactive = round(mean(days_since_last_order, na.rm = TRUE), 0),
    avg_spent         = round(mean(total_spent, na.rm = TRUE), 2),
    total_revenue     = round(sum(total_spent,  na.rm = TRUE), 0)
  )

knitr::kable(at_risk_stats,
             caption = "At Risk Segment Profile",
             col.names = c("Customers",
                           "Avg Days Inactive",
                           "Avg Spent (R$)",
                           "Total Revenue (R$)"))
```

**Win-back campaign structure:**

- Day 1: Personalized email — "We miss you" 
  with 10% discount code
- Day 15: Follow-up email with 
  "Top picks based on your last order"
- Day 30: Final offer — 
  15% discount with urgency message
- Day 45: Move to "Lost" if no response

---

## Recommendation 3 — Protect Champions Segment

**Priority: HIGH**

**Based on:** Champions = 6,473 customers, 
avg CLV R$122 — 8.6x more valuable than Lost

**The Problem:**

Champions are the most valuable customers 
but receive no special treatment currently. 
Without recognition, even Champions can 
become At Risk over time.

**The Recommendation:**

Create a VIP program exclusively for Champions:

```{r champions-profile}
champions_profile <- churn_data %>%
  left_join(
    rfm_scored %>% select(customer_unique_id, segment),
    by = "customer_unique_id"
  ) %>%
  filter(segment == "Champions") %>%
  summarise(
    customers     = n(),
    avg_orders    = round(mean(total_orders,           na.rm = TRUE), 2),
    avg_spent     = round(mean(total_spent,            na.rm = TRUE), 2),
    avg_recency   = round(mean(days_since_last_order,  na.rm = TRUE), 0),
    total_revenue = round(sum(total_spent,             na.rm = TRUE), 0)
  )

knitr::kable(champions_profile,
             caption = "Champions Segment Profile",
             col.names = c("Customers", "Avg Orders",
                           "Avg Spent (R$)",
                           "Avg Days Since Order",
                           "Total Revenue (R$)"))
```

**VIP program elements:**

- Early access to new products and sales
- Free shipping on all orders
- Dedicated customer support
- Birthday discount voucher
- Quarterly "thank you" gift voucher

---

## Recommendation 4 — Fix Post-Purchase Engagement

**Priority: MEDIUM**

**Based on:** Month 1 retention = 0.47%, 
no engagement after purchase drives churn

**The Problem:**

After a customer places an order, Olist 
has no touchpoint strategy. The customer 
completes their purchase and disappears — 
with no reminder, recommendation, or 
reason to return.

**The Recommendation:**

Implement a post-purchase email sequence 
for every customer:

```{r email-sequence}
email_seq = data.frame(
  Day = c("Day 3", "Day 7", "Day 21", 
          "Day 45", "Day 90"),
  Email = c(
    "Delivery confirmation + review request",
    "Thank you + similar product recommendations",
    "Category restock reminder",
    "Exclusive discount — next purchase",
    "Re-engagement offer if no purchase"
  ),
  Goal = c(
    "Confirm satisfaction",
    "Drive product discovery",
    "Trigger repeat need",
    "Convert to repeat buyer",
    "Prevent full churn"
  )
)

knitr::kable(email_seq,
             caption = "Recommended Post-Purchase Email Sequence")
```

---

## Recommendation 5 — Focus on High Frequency Categories

**Priority: MEDIUM**

**Based on:** Low repeat rate partly driven 
by low-frequency product categories

**The Problem:**

Olist's top categories (furniture, bed/bath, 
electronics) are naturally low-frequency 
purchases. Customers buy once and have no 
need to return for months or years.

**The Recommendation:**

Strategically expand into high-frequency 
categories to create natural repeat 
purchase opportunities:

```{r category-recommendation}
high_freq = data.frame(
  Category = c(
    "Health & Beauty (refills)",
    "Pet Food & Supplies",
    "Office Supplies",
    "Baby Products",
    "Sports Nutrition"
  ),
  Purchase_Frequency = c(
    "Monthly", "Weekly/Monthly",
    "Monthly", "Weekly",
    "Monthly"
  ),
  Retention_Impact = c(
    "High", "Very High",
    "Medium", "Very High",
    "High"
  )
)

knitr::kable(high_freq,
             caption = "Recommended High-Frequency Categories",
             col.names = c("Category", 
                           "Purchase Frequency",
                           "Expected Retention Impact"))
```

---

## Recommendation Priority Matrix

```{r priority-matrix}
priority = data.frame(
  Recommendation = c(
    "Launch Loyalty Program",
    "At Risk Win-Back Campaign",
    "Protect Champions — VIP Program",
    "Post-Purchase Email Sequence",
    "Expand High-Frequency Categories"
  ),
  Priority = c(
    "HIGH", "HIGH", "HIGH",
    "MEDIUM", "MEDIUM"
  ),
  Timeline = c(
    "0-3 months", "Immediate",
    "0-3 months", "0-1 month",
    "3-6 months"
  ),
  Revenue_Impact = c(
    "R$ 690,000+",
    "R$ 2,077,785",
    "R$ 789,972 protected",
    "Increase repeat rate",
    "Long-term retention"
  )
)

knitr::kable(priority,
             caption = "Business Recommendation Priority Matrix",
             col.names = c("Recommendation", "Priority",
                           "Timeline", "Expected Impact"))
```

---

## Conclusion

```{r conclusion}
cat("This analysis demonstrates that Olist's\n")
cat("core challenge is not customer satisfaction\n")
cat("(avg review: 4.16/5) but platform loyalty.\n\n")
cat("Three immediate actions can protect and\n")
cat("recover significant revenue:\n\n")
cat("1. Win-back At Risk segment → R$2.07M CLV uplift\n")
cat("2. Protect Champions → R$789,972 revenue protected\n")
cat("3. Loyalty program → estimated R$690,000+ uplift\n\n")
cat("Combined potential impact: R$3.5M+\n")
```

